Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-06 paper/sec-mva.tex
work on paper

To investigate this, we now consider a variant of the analysis used in
Table~\ref{tab:resCutflow} where the $m_H$ window criterion has been relaxed to $80 < m_H < 170$.
%
Firstly the same analysis is repeated with the larger $m_H$ window, with no smearing at all.
%
This is then compared to the same analysis but with a Gaussian smearing with $\sigma=10$ GeV applied to the dijet invariant mass used in the MVA.
%
In the left panel of Fig.~\ref{fig:invMsmear} the smearing is demonstrated.
%
Both with and without smearing, the  invariant mass distribution of the
Higgs candidates is still the most discriminative variable.
%
This can be seen by comparing with   with the corresponding distribution with smearing in
  Fig.~\ref{fig:nnweights}.

>>>>

To investigate this, we now consider a variant of the analysis used in
Table  where the $m_H$ window criterion has been relaxed to $80 < m_H < 170$.
%
Firstly the same analysis is repeated with the larger $m_H$ window, with no smearing at all.
%
This is then compared to the same analysis but with a Gaussian smearing with $\sigma=10$ GeV applied to the dijet invariant mass used in the MVA.
%
In the left panel of Fig.~\ref{fig:invMsmear} the smearing is demonstrated.
%
Both with and without smearing, the  invariant mass distribution of the
Higgs candidates is still the most discriminative variable.
%
This can be seen by comparing with   with the corresponding distribution with smearing in
  Fig.~\ref{fig:nnweights}.

### 2015-07-06 paper/sec-results.tex
work on paper

In order to compare with previous results, it is interesting to
study how our results change if we consider only the QCD $4b$
multi-jet background, but ignore the $2b2j$ and $4j$ backgrounds,
that is, we ignore the contribution from the fakes.
%
For the boosted category, the results are shown in
Table~\ref{table:cutflowboosted4B}, which is the analog of
Table~\ref{table:cutflowboosted} but with only the QCD
$4b$ background taken into account.
%
As we can see, these results indicate that given the similarity of the final states
in signal and background events in these cases, the signal significance is
relatively stable at various stages of the cut-flow.
%
As compared to the case in which all backgrounds are taken into account, we
now get a factor two smaller backgrounds: we conclude that in the boosted category
the effect of the fakes is non-negligible, with their contribution being
comparable to that of the irreducible $4b$ QCD multi-jet background.

>>>>

In order to compare with previous results, it is interesting to
study how our results change if we consider only the QCD $4b$
multi-jet background, but ignore the $2b2j$ and $4j$ backgrounds,
that is, we ignore the contribution from the fakes.
%
For the boosted category, the results are shown in
Table~\ref{table:cutflow4B}, which is the analog of
Table~\ref{table:cutflow} but with only the QCD
$4b$ background taken into account.
%
As we can see, these results indicate that given the similarity of the final states
in signal and background events in these cases, the signal significance is
relatively stable at various stages of the cut-flow.
%
As compared to the case in which all backgrounds are taken into account, we
now get a factor two smaller backgrounds: we conclude that in the boosted category
the effect of the fakes is non-negligible, with their contribution being
comparable to that of the irreducible $4b$ QCD multi-jet background.
